Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
fix peignier
add temp to abs

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. <!-- and vary within
and across seasons.--> Multilayer networks promise the explicit integration of
the social, spatial and temporal contexts. Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains an
important gap in our understanding of the influence of scale on animal social
networks. We discuss ways of considering social, spatial and temporal scale in
the context of multilayer caribou social networks. <!--We also present
perspectives on future development and applications of scale in multilayer
networks with respect to: phenotypes and individual fitness, movement ecology
and collective movement, and habitat selection and space use.--> Effective
integration of social and spatial processes, including biologically meaningful
scales, within the context of animal social networks is an emerging area of
research. We incorporate perspectives on how the social environment and spatial
processes are linked across scales in a multilayer context.

@@

The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information.
We found increased edge overlap and graph strength in fall, winter and spring
(approximately October - June) than in summer (approximately June - October)
(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
to seasons of heterogeneous resource availability [Peignier_2019]. This analysis
could be extended using time-aggregated networks and a moving-window approach for
informing time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
explicitly considering the temporal context of social interactions in separate
layers, multilayer networks provide a detailed and dynamic perspective of animal
social systems. For example, female mandrill (*Mandrillus sphinx*) sociality is
more completely represented by temporal multilayer networks than aggregated
networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
to temperature and breeding activity. Finally, it is crucial to include
sufficient data within sampling periods or time windows to construct robust
networks [@Farine_2017; @Proskurnikov_2017]. With increasing number of
observations, we found variance decreased in edge overlap and multidegree across
habitat layers as well as in graph strength within habitat layers (Figure
\@ref(fig:nobs)). In addition, less common relationships were recorded with
increasing number of observations, demonstrating the value of this form of sensitivity analysis.

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. Lastly,
sociality can vary within and across seasons. <!-- and vary within
and across seasons.--> Multilayer networks promise the explicit integration of
the social, spatial and temporal contexts. Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains an
important gap in our understanding of the influence of scale on animal social
networks. We discuss ways of considering social, spatial and temporal scale in
the context of multilayer caribou social networks. <!--We also present
perspectives on future development and applications of scale in multilayer
networks with respect to: phenotypes and individual fitness, movement ecology
and collective movement, and habitat selection and space use.--> Effective
integration of social and spatial processes, including biologically meaningful
scales, within the context of animal social networks is an emerging area of
research. We incorporate perspectives on how the social environment and spatial
processes are linked across scales in a multilayer context.

@@

The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information.
We found increased edge overlap and graph strength in fall, winter and spring
(approximately October - June) than in summer (approximately June - October)
(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
to seasons of heterogeneous resource availability [@Peignier_2019]. This analysis
could be extended using time-aggregated networks and a moving-window approach for
informing time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
explicitly considering the temporal context of social interactions in separate
layers, multilayer networks provide a detailed and dynamic perspective of animal
social systems. For example, female mandrill (*Mandrillus sphinx*) sociality is
more completely represented by temporal multilayer networks than aggregated
networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
to temperature and breeding activity. Finally, it is crucial to include
sufficient data within sampling periods or time windows to construct robust
networks [@Farine_2017; @Proskurnikov_2017]. With increasing number of
observations, we found variance decreased in edge overlap and multidegree across
habitat layers as well as in graph strength within habitat layers (Figure
\@ref(fig:nobs)). In addition, less common relationships were recorded with
increasing number of observations, demonstrating the value of this form of sensitivity analysis.
